A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-19 tex/codatadp.tex
more

The mapping $\Val$ is computed as follows.
%
For each equivalence class $\ec{x}$, we associate a fresh variable $\Var{\ec{x}}$ of the same type as $x$
%not occurring in $\tEc$,
and let $\Val\ec{x} = \Var{\ec{x}}$.
Thus, there are initially no constraints on the values for any equivalence class $\ec{x}$.
The mapping $\Val$ is then modified by applying the following rule exhaustively:
\[
\hbox{\(
\inferrule{
  \Var{\ec{x}} \in \FV( \Val )
  \quad
  \const{C}( t_1, \ldots, t_n ) \in \ec{x}
  \quad
  \const{C} \in \Ctr
}{
  \Val := \Val \{ \Var{\ec{x}} \mapsto \mu \Var{\ec{x}}.\; \const{C}( \Var{\ec{t_1}}, \ldots, \Var{\ec{t_n}} ) \}
}
\)
\rn{Update}}
\]
In the rule, $\FV( \Val )$ denotes the union of the free variables occurring in $\Val$'s range.
It is straightforward to see that the height of terms produced as a result of this update
is bounded by the number of equivalence classes of $\Ec$,
and thus our construction of $\Val$ is terminating.

>>>>

The mapping $\Val$ is computed as follows.
%
For each equivalence class $\ec{x}$, we associate a fresh variable $\Var{\ec{x}}$ of the same type as $x$
%not occurring in $\tEc$,
and let $\Val\ec{x} = \Var{\ec{x}}$.
Thus, there are initially no constraints on the values for any equivalence class $\ec{x}$.
The mapping $\Val$ is then modified by applying the following rule exhaustively:
\[
\hbox{\(
\inferrule{
  \Var{\ec{x}} \in \FV( \Val )
  \quad
  \const{C}( t_1, \ldots, t_n ) \in \ec{x}
  \quad
  \const{C} \in \Ctr
}{
  \Val := \Val \{ \Var{\ec{x}} \mapsto \mu \Var{\ec{x}}.\; \const{C}( \Var{\ec{t_1}}, \ldots, \Var{\ec{t_n}} ) \}
}
\)
\rn{Refine}}
\]
$\FV( \Val )$ denotes the union of the free variables occurring in $\Val$'s range.
It is straightforward to see that the height of terms produced as a result of this update
is bounded by the number of equivalence classes of $\Ec$,
and thus the construction of $\Val$ will terminate.
